%the margin option causes section titles to appear to the left of body text.
\documentclass[line, margin, 11pt]{res}

\author{Zhongfu Gao}
\title{Resume}
\date{\today}

\begin{document}

\renewcommand{\namefont}{ \LARGE \bf } %% name font
\name{Zhongfu Gao}
\address{{\bf Email: }joshuafufu@gmail.com}
\address{{\bf Mobile: }(+86)15921928229}

\begin{resume}

\section{Objective}
Software Engineer

\section{Education}
{\bf B.S. Software Engineering}\\
Fudan University\hfill {\it Sep 2006 - July 2010}\\
{\sl Major in software engineering}

\section{Skills}
{\bf Computer languages:} Java, C, Shell Scripting, Python, JavaScript, Lisp, Sql\\
{\bf IDEs:} Eclipse, Emacs\\
{\bf Databases:} MySQL, Oracle\\
{\bf English:} CET-6 pass


\section{Experience}

%% experience 1
{\bf Software Engineer}\hfill {\it Dec 2011 - Current}\\
{\sl Company:} Ericsson, Shanghai\\
{\sl Projects experience:} Conference Handler\\
{\sl Responsibilities} \& {\sl Gains:}
\begin{itemize}
\item Developed several features on conference handler which is a back-end server based on J2EE, including smart link, email supporting, short message sending and recurrent meeting.
\item Developed and worked with agile and TDD. Trained on agile, pair programming and TDD.
\item Enhanced Java programming skills, and got a better understanding and practice on design patterns.
\item Kept working on code refactoring step by step to enhance the code quality. It both had benefits on products and myself.
\item Worked positively in learning new techniques such as learning python to improve CI(continuous integration) and simplify function tests.
\item Achieved experiences on communicating with foreigners, which enhanced both English and communication skills.
\end{itemize}

%% experience 2
{\bf Software Engineer}\hfill {\it Mar 2011 - Dec 2011}\\
{\sl Company:} Bank of China, Shanghai\\
{\sl Projects experience:} FXBT\\
{\sl Responsibilities} \& {\sl Gains:}
\begin{itemize}
\item Designed and Developed FXBT which is roughly a foreign currency exchanging system based on C, Java and Sql languages.
\item Developed from the very beginning, which gave me an overall view on how software developing runs in waterfall model.
\item Mainly focused on designing and developing the feature of foreign currency exchanging and accounting.
\end{itemize}

%% experience 3
{\bf Software Engineer}\hfill {\it Oct 2010 - Dec 2011}\\
{\sl Company:} Bank of China, Shanghai\\
{\sl Projects experience:} TPCC, ECCC\\
{\sl Responsibilities} \& {\sl Gains:}
\begin{itemize}
\item Developed and maintained TPCC \& ECCC based on C, Java and Sql languages.
\item Absorbed much knowledge about banking and got a deep understanding of the overall architecture of the banking system.
\item Developed with WebSphere, IBM CICS and Oracle.
\item Enhanced the ability of problem solving and mental capacity when facing problems.
\item Gained experience to work under high pressures of customers.
\item Improved the performance of TPCC system by improving the persistence layer and making better usage of indexes of Oracle db.
\item Learned and shared knowledge on performance tuning with Oracle db in customers' system in the department.
\item Developed the feature of integrating virtual stock account with other kinds of accounts in TPCC and ECCC.
\end{itemize}

%% experience 4
{\bf Software Engineer}\hfill {\it Jul 2010 - Oct 2010}\\
{\sl Company:} Bank of China, Shanghai\\
{\sl Projects experience:} BPS\\
{\sl Responsibilities} \& {\sl Gains:}
\begin{itemize}
\item Developed and maintained the web portal of BPS system which was used for bank tellers to check accounts everyday automatically based on Java, Jsp, JavaScript, Hibernate and Spring.
\item Promoted the ability in communications and co-operations with customers and teams.
\end{itemize}

\section{Personal}
{\bf Computers:} Passionate about computer techniques. In spare time, I have paid much time on learning new techniques.\\
{\bf Character:} Friendly, faithful and honest.\\
{\bf Hobbies:} Love several kinds of sports such as basketball and football, and has good team spirit.\\
\end{resume}
\end{document}
